---
title: "Sleep Analysis"
output: html_document
date: "2024-08-03"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
############################
## Introduction ##
############################

# This is  a sample starter script and to use R 

#Installing and loading the tidyverse
install.packages('tidyverse')
```{r load the tidyverse}
library(tidyverse)
```
#####################
## Loading The CSV files ##
#####################

# Creating a dataframe and named it 'daily_activity' 

```{r load the csv files}

daily_activity <- read.csv("C:\\Users\\Anjali\\OneDrive\\文档\\archive2\\mturkfitbit_export_3.12.16-4.11.16\\Fitabase Data 3.12.16-4.11.16\\dailyActivity_merged.csv")
```

# Creating another dataframe for the sleep data. 
```{r load another file} 
sleep_day <- read.csv("C:\\Users\\Anjali\\OneDrive\\文档\\archive2\\mturkfitbit_export_4.12.16-5.12.16\\Fitabase Data 4.12.16-5.12.16\\sleepDay_merged.csv")
```
#########################
## Exploring a few key tables ##
#########################

# Daily_activity data.
```{r }
head(daily_activity)
```

# Identifing all the columns in the daily_activity data.
```{r}
colnames(daily_activity)
```

# The sleep_day data.
```{r}
head(sleep_day)
```

# Identifing all the columns in the sleep_day data.
```{r}
colnames(sleep_day)
```

#####################################
## Understanding some summary statistics ##
#####################################


```{r}
n_distinct(daily_activity$Id)
n_distinct(sleep_day$Id)
```

# Observations on data
```{r}
nrow(daily_activity)
nrow(sleep_day)
```
  
# For the daily activity dataframe:
```{r}
daily_activity %>%  
  select(TotalSteps,
         TotalDistance,
         SedentaryMinutes) %>%
  summary()
```

# For the sleep dataframe:
```{r}
sleep_day %>%  
  select(TotalSleepRecords,
         TotalMinutesAsleep,
         TotalTimeInBed) %>%
  summary()
```


##########################
## Plotting a few explorations ##
##########################


```{r}
ggplot(data=daily_activity, aes(x=TotalSteps, y=SedentaryMinutes)) + geom_point()
```

```{r}

ggplot(data=sleep_day, aes(x=TotalMinutesAsleep, y=TotalTimeInBed)) + geom_point()
```


  
##################################
## Merging these two datasets together ##
##################################
```{r}
combined_data <- merge(sleep_day, daily_activity, by="Id")
```
# The no of participates are: 24 According to observation

```{r}
n_distinct(combined_data$Id)
```
